---
title: 'Second network analysis #NZES2015'
author: "Olivia Burge"
date: "21 November 2015"
output: html_document
---

Network analysis to try to see how relationships changed over the course of the conference. The first job though is to try to get a decent visualisation of the end of conference network.

## Data in 

```{r}
nodes <- read.csv("../../Dropbox/node xl/saturday_nodes.csv",
                   stringsAsFactors=FALSE)
links <- read.csv("../../Dropbox/node xl/vertices.csv",
                   stringsAsFactors=FALSE)
```

## Packages

```{r}
#  install.packages("igraph")
#  install.packages("network") 
#  install.packages("sna")
#  install.packages("ndtv")

require(igraph)

require(network)

require(sna)

require(ndtv)
````

## Quick look at data

```{r}
nrow(nodes); length(unique(nodes$Vertex))
nrow(links); nrow(unique(links[,c("Vertex.1", "Vertex.2")]))
head(nodes)
head(links)
````

## Create network

```{r}
net <- graph.data.frame(links, nodes, directed=T)
net

E(net)       # The edges of the "net" object
V(net)       # The vertices of the "net" object
E(net)$   # Edge attribute "type"
V(net)$Location # Vertex attribute "media"

# You can also manipulate the network matrix directly:

net[1,]
net[5,7]

plot(net)

net <- simplify(net, remove.multiple = F, remove.loops = T)

plot(net)
plot(net, edge.arrow.size=.1, edge.curved=.2)


# Set edge color to light gray, the node & border color to orange 
# Replace the vertex label with the node names stored in "media"
plot(net, edge.arrow.size=.01, edge.color="orange",
     vertex.color="orange", vertex.frame.color="#ffffff",
     vertex.label.color="black") 



# Generate colors base on media type:
colrs <- c("gray50", "tomato", "gold")
V(net)$color <- colrs[V(net)$media.type]

# Compute node degrees (#links) and use that to set node size:
deg <- igraph::degree(net, mode="all")
#V(net)$size <- ifelse(deg > 1, log(deg), 0.5)
V(net)$size <- sqrt(deg)
plot(net, rescale=F, layout=l* 1.1)
# We could also use the audience size value:
require(scales)
V(net)$size <- scales::rescale(x = betweenness(net), to = c(0, 8))

# The labels are currently node IDs.
# Setting them to NA will render no labels:
V(net)$label <- NA

# Set edge width based on weight:
E(net)$width <- E(net)$Edge.Weight/6

#change arrow size and edge color:
E(net)$arrow.size <- .01
E(net)$edge.color <- "gray80"
E(net)$width <- 1+E(net)$Edge.Weight/12
plot(net) 

#Subset the data. If we want to exclude people who are in the network only tangentially (participate in one or two relationships only)
# we can exclude the by subsetting the graph on the basis of the 'degree':

bad.vs<-V(net)[degree(net)<3] #identify those vertices part of less than three edges
net <-delete.vertices(net, bad.vs) #exclude them from the graph
plot(net)

V(net)$frame.color <- "white"
V(net)$color <- "orange"
l <- layout.fruchterman.reingold(net)
l <- layout.norm(l, ymin=-1, ymax=1, xmin=-1, xmax=1)
plot(net, rescale=F, layout=l*1.9, vertex.label = V(net)$name,
     vertex.shape = "none", vertex.label.cex = 0.5)

```


## Trying to create an animated one:

### Aim: 

To create an animated network that:
- when you click on a node, it provides the person's name,
their betweenness, their degree.
- nodes sized by their betweenness 
- exclude the ring around the edge (maybe)
- put colour, based on something, but not sure what. 
    - maybe cluster based on degrees, centrality, etc? 
- would be cool
    

```{r}
require(network)
require(dplyr)
net3 <- network(links,  vertex.attr = nodes %>%
                  select(id = Vertex, Followed, Followers, Tweets, Favorites), 
                matrix.type="edgelist",
                loops=F, multiple=F, ignore.eval = F)
plot(net3)

bad.vs<-net3[degree(net3)<3] #identify those vertices part of less than three edges
net3 <-delete.vertices(net3, bad.vs) #exclude them from the graph
plot(net3)
```


That was ok, but that's not going to be interactive. Need to make a network that will be.

```{r}
detach(package:network)
detach(package:igraph)
require(ndtv)

net3

net4 <- networkDynamic(net3)
```


## An interactive one?

```{r}


render.d3movie(net4, usearrows = F, displaylabels = F, 
               bg="#111111", 
       vertex.border="#ffffff", 
       #vertex.col =  net4 %v% "col",
       vertex.cex = log(net4 %v% "Followed"), 
       edge.lwd = (net4 %e% "weight")/3, 
       edge.col = '#55555599',
       vertex.tooltip = paste("<b>Name:</b>", (net4 %v% 'Vertex') , "<br>",
                              "<b>Tweets:</b>", (net4 %v% 'Tweets')),
       edge.tooltip = paste("<b>Edge type:</b>", (net4 %e% 'type'), "<br>", 
                            "<b>Edge weight:</b>", (net4 %e% "weight" ) ),
       launchBrowser=T, filename="Media-Network.html",
       output.mode='HTML')  
````
