---
title: "Tweets from nzes2015"
author: "Olivia Burge"
date: "20 November 2015"
output: html_document
---

## Summary of NZES 2015 tweets
Tweets collected at 6 pm, Friday 20 November 2015 from Cass Field Station writer's retreat. I've saved the tweets as a dataframe, you would need to set up a twitter account and scrape twitter to redo the analysis from scratch yourself.

```{r, echo = FALSE, message=FALSE, warning=FALSE}
require(wesanderson)
require(wordcloud)
require(ggplot2)
require(dplyr) ## you'll need to install this if you don't have it already
#tweets_df <- read.csv("nzes2015tweets.csv")
load("raw_tweets.Rdata")
```

There were `r nrow(dt_tweets)` tweets and retweets at NZES2015, and `r nrow(dt_tweets %>% filter(isRetweet == FALSE))` unique tweets. `r length(unique(dt_tweets$screenName))` different users tweeted using the NZES2015 hashtag. 

## Tweeting times

```{r, echo = FALSE}

ggplot(dt_tweets, aes(x = created)) + 
  scale_x_datetime() +
  geom_histogram(binwidth = 1600) + 
  theme_bw()  +
  labs(x = "Date", y = "Tweets", title = "#NZES2015 tweets")

```


## Most prolific tweeters
I've excluded retweeting for this, and only included those who tweeted more than five times with the hashtag

```{r, echo = FALSE}
dt_tweets_users <- dt_tweets %>%
  filter(isRetweet == "FALSE") %>%
  group_by(screenName) %>%
  summarise(ntweets = n()) %>%
  arrange(desc(ntweets)) %>%
  filter(ntweets > 5)
dt_tweets_users

ggplot(dt_tweets_users, aes(x = ntweets, 
                            y = reorder(screenName, ntweets))) +
  geom_point() +
  scale_x_log10()+
  labs(y = "Screen name", x = "Tweet count")+
  theme_bw()
```


## Most activity-provoking tweeters

I've plotted this by the average number of retweets and favourites a user got. The number of tweets they wrote using the hashtag is included in blue/green at the right of the graph.

### Retweeted users 

```{r, echo = FALSE}
tweeters <- dt_tweets %>%
  filter(isRetweet == "FALSE") %>%
  group_by(screenName) %>%
  summarise(mean_retweets = mean(retweetCount),
            se_retweets = sd(retweetCount)/sqrt(length(retweetCount)),
            mean_favourites = mean(favoriteCount),
             se_favourites = sd(favoriteCount)/sqrt(length(favoriteCount)),
            total_tweets = n()) %>%
  filter(total_tweets > 5) 

tweeters2 <- tweeters %>%
  arrange(desc(mean_retweets)) %>% 
  select(screenName, mean_retweets, se_retweets, total_tweets) %>%
  slice(1:5)

ggplot(tweeters2, aes(x = reorder(screenName, mean_retweets), y = mean_retweets)) +
    geom_errorbar(aes(ymin = mean_retweets - se_retweets,
                    ymax = mean_retweets + se_retweets),
                width = 0.2, colour = "grey") +
  geom_point(size = 3) +
  coord_flip() +
  theme_bw() +
  geom_text(aes(x = screenName, y = 6, label = total_tweets),
            colour = "darkblue", size = 5) +
  labs(y = "Retweets (mean \U00b1 SE)", x = "Twitter handle") +
  ggtitle("Most retweeted users")

````

### Most favourited users

```{r, echo = FALSE}
tweeters3 <- tweeters %>%
  arrange(desc(mean_favourites)) %>% 
  select(screenName, mean_favourites, se_favourites, total_tweets) %>%
  slice(1:5)

ggplot(tweeters3, aes(x = reorder(screenName, mean_favourites), y = mean_favourites)) +
    geom_errorbar(aes(ymin = mean_favourites - se_favourites,
                    ymax = mean_favourites + se_favourites),
                width = 0.2, colour = "grey") +
  geom_point(size = 3) +
  coord_flip() +
  theme_bw() +
  geom_text(aes(x = screenName, y = 8.5, label = total_tweets),
            colour = "forestgreen", size = 5) +
  labs(y = "Favourites (mean \U00b1 SE)", x = "Twitter handle")+
  ggtitle("Most favourited users")
```

## Most talked about tweets
I've ranked these on how much they were retweeted, but display the 'favorite' count too.

```{r, echo = FALSE}
most_liked_tweets <- dt_tweets %>% 
  filter(isRetweet == "FALSE" & retweetCount > 0) %>%
  arrange(desc(retweetCount)) %>%
  slice(1:3) %>%
  select(screenName,  retweetCount, favoriteCount, text)
```

```{r, results = "asis", message = FALSE, echo = FALSE}
require(xtable)
print.xtable(xtable(most_liked_tweets, digits = 0), type = "html", include.rownames = FALSE)
```


## And, a final word cloud
.. not shown, you'll have to use the code to knit your own! (it's a bit big)

```{r, echo = FALSE, message=FALSE, warning = FALSE}
mytweets2 <- dt_tweets %>%
  select(text) %>%
  gsub("â", "", .) %>%
  gsub("(@|\\#)\\w+", "", .) %>%  ## remove mentions/hashtags
  gsub("https?\\:\\/\\/\\w+\\.\\w+(\\/\\w+)*", "", .) %>% ## remove urls
  gsub("https\\:\\/\\/\\w+\\.\\w+(\\/\\w+)*", "", .) %>% ## remove urls
  gsub("\\bthe\\b", "", .) %>% ## remove the
  gsub("amp", "", .) %>%  ## remove &
  gsub("https:â\u0080", "", .) %>%
  gsub("Hmm, â\u0080¦", "", .) %>%
  gsub("\\bspp\\b", "species", .) %>% ## replace spp by species
  # filter(!isRetweet) %>%
  paste(collapse = "") %>%
  iconv(., from = "latin1", to = "UTF-8", sub = "")

pal <- wes_palette("Royal2", 9, type = "continuous") #

wordcloud(words = mytweets2, max.words = 100, colors = pal, random.order = FALSE, scale = c(3, .5))

````